\documentclass[letterpaper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{cmbright} % added from otherfile.tex
\usepackage[sf]{libertine} % added from otherfile.tex
% Remove or comment out the Georgia font setting
% \fontfamily{Georgia}\selectfont
% \fontseries{m}\selectfont
%...

\usepackage{latexsym}
\usepackage{microtype}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\renewcommand{\bfseries}{\fontseries{b}\selectfont}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\small\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands


\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \footnotesize\textbf{#1} & \footnotesize #2 \\
      \footnotesize\textit{#3} & \footnotesize\textit{#4} \\
    \end{tabular*}\vspace{-6pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\scriptsize$\cdot$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in, labelsep=.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\LARGE \scshape \bfseries Vansh Singh} \\ \vspace{1pt}
    I’m a Software Developer specializing in building and designing exceptional digital experiences. \\ \vspace{1pt}
    \small +1 780 708 1340 $|$ \href{mailto:vansh2@ualberta.ca}{\underline{vansh2@ualberta.ca}} $|$ 
    \href{https://linkedin.com/in/easyvansh/}{\underline{linkedin.com/in/easyvansh}} $|$
    \href{https://github.com/easyvansh}{\underline{github.com/easyvansh}}
\end{center}
%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Alberta}{Edmonton, AB}
      {Bachelors of Science (BSC), Computer Science}{Aug. 2021 -- Current}
  \resumeSubHeadingListEnd

%-----------HIGHLIGHTS-----------
\section{HIGHLIGHTS}
  \resumeSubHeadingListStart
    \resumeItem{Robust foundation in computer science concepts such as Object Oriented Programming Pradaigms and proficiency in front-end and back-end development, proficient in frameworks such as React, Express, Node.js, and databases like SQL and MongoDB.}
    \resumeItem{Proficient in cloud computing (Firebase, GCP), dedicated to developing scalable applications and adhering to best practices in code maintainability, optimization, and documentation.}
    \resumeItem{Committed to lifelong learning in evolving tech landscapes, coupled with strong interpersonal and communication skills for effective teamwork in diverse environments.}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{PROJECTS}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://github.com/easyvansh/shop-squad}{\textbf{Shop Squad }}}{\textbf{React Native, Redux Toolkit, Express JS and Stripe}}
      \resumeItemListStart
        \resumeItem{Spearheaded the development of a cutting-edge React Native application, bolstering the group-buy functionality for a dynamic startup.}
        \resumeItem{Fortified the platform with robust security measures, incorporating secure payment gateways(stripe) and seamless user authentication.}
        \resumeItem{Elevated user engagement and satisfaction by crafting an aesthetically pleasing user interface and optimizing the overall user experience.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://github.com/easyvansh/Weather-App}{\textbf{Weather App}}}{\textbf{React Native, Weather API and Geolocation}}
      \resumeItemListStart
        \resumeItem{Engineered a real-time mobile application using React Native, providing up-to-the-minute weather updates.}
        \resumeItem{Seamlessly integrated Weather APIs to ensure precise weather data retrieval.}
        \resumeItem{Implemented advanced Geolocation functionality, enabling automatic detection of the user's current location for a seamless experience.}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\href{https://github.com/easyvansh/Film-Wizard}{\textbf{Film Wizard}}}{\textbf{Python, Streamlit, Scikit, Pandas and NumPy}}
      \resumeItemListStart
        \resumeItem{Developed a movie recommendation system web application using the TMDB Movies Dataset, easing the movie-selection process experience for users.}
        \resumeItem{Implemented TF-IDF algorithms to deliver personalized movie suggestions based on user preferences and viewing history.}
        \resumeItem{Designed and implemented a friendly GUI, ensuring seamless navigation.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://github.com/easyvansh/QuickWit}{\textbf{QuickWit}}}{\textbf{Python, Tkinter and PyMuPDF}}
      \resumeItemListStart
        \resumeItem{Developed a feature-rich speed reading application, utilizing the Rapid Serial Visual Presentation (RSVP) technique to significantly boost reading speed and comprehension.}
        \resumeItem{Designed a user-friendly GUI for loading PDFs and text documents, allowing easy start, stop, and resume reading.}
        \resumeItem{Actively contributed to the open-source community by developing Quick Wit and making it available for public use.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/easyvansh/To-Do-List}{\textbf {To Do List Dashboard}}}{\textbf{React JS}}
      \resumeItemListStart
        \resumeItem{Developed a highly interactive and user-friendly to-do list application using React JS, enabling efficient task management and organization.}
        \resumeItem{Implemented advanced features like task categorization, deadlines, and priority tagging, allowing users to manage tasks more effectively.}
        \resumeItem{Integrated responsive design principles to ensure a seamless user experience across various devices and screen sizes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% 
%-----------SKILLS-----------
\section{ SKILLS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Languages:} Python, C/C\small{++}, Javascript, SQL, MongoDB, HTML/CSS, Shell}{}
      \resumeProjectHeading
          {\textbf{Frameworks:} React/Next JS, React Native, Node JS, Express JS, Pandas, Selenium, Numpy}{}
      \resumeProjectHeading
          {\textbf{Developer Tools:} Git, Linux, Google Firebase, Google Cloud Platform,  MySQL, Android Studio}{}
    \resumeSubHeadingListEnd

%
%-----------Honors and Awards-----------
\section{ HONORS AND AWARDS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{International Student Scholarship:} Awarded by University of Alberta.}{}
      \resumeProjectHeading
          {\textbf{Second Ranked Team:} Runner Ups at the Calgary Youth Hackathon for developing a web tool for seeking mental health support.}{}
    \resumeSubHeadingListEnd

%
%-----------OTHER INTERESTS-----------
\section{OTHER INTERESTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Volunteer Work:} Participated in Conversation Club and Debate Club.}{}
      \resumeProjectHeading
          {\textbf{Reading:} Enthusiastic reader of Non-fiction and Classic literature.}{}
      \resumeProjectHeading
          {\textbf{Technology:} Keen interest in Artificial Intelligence and Machine/Deep Learning.}{}
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
